Project 1 Checkpoint

### 2015-02-03 project1/checkpoint/main.tex
Adding figures to the file
Finishing up the assumptions section

\usepackage{url, hyperref}

@@

The distribution of car arrival is very important, but has been difficult to model.

\subsection{Simulation Output}

@@

>>>>

\usepackage{url, hyperref, graphicx}

@@

\begin{figure}
\begin{center}  
\includegraphics[width=4in]{../northbound.png}  
\caption{\small \sl Northbound Arrival Intervals \label{fig:northbound_arrival}}  
\end{center}  
\end{figure}

\begin{figure}  
\begin{center}
\includegraphics[width=4in]{../southbound.png}  
\caption{\small \sl Southbound Arrival Intervals \label{fig:southbound_arrival}}  
\end{center}  
\end{figure}

The distribution of car arrival is very important, but has been difficult to model. The arrival intervals between 
northbound and southbound cars are provided in \ref{fig:northbound_arrival} and \ref{fig:southbound_arrival}.
Model fitting was attempted for both $\Gamma$ and $\Gamma$ mixture models on the raw data, but resulted in poor
fits. Furthermore, pruning outliers via the common interquartile range approach, where values are rejected when
they lie outside of $median + 1.5IQR$, where $IQR$ is the interquartile range $Q_3 - Q_1$.

So, instead we'll take a simpler approach and assume the ``true distribution`` is modeled by what was observed,
and simply use the observed frequency distribution as our input distribution. As the project progresses we can
refine this model.

The current light timing of the system is known, and provided in \cite{ngsim}, but we'll allow the user to set
those values dynamically via a UI.

\subsection{Simulation Output}
The most important statistic we'll want to collect during the simulation is the thoughput of the simulation. We'll
want to observe how the light timing affects the average travel time for cars. It will also to see how variable this
is. For instance, do cars travelling on Peachtree St. have similar travel times, despite their arrival time, or does
their arrival drastically lengthen their time to travel the stretch of road we are modeling.

@@

Another simplification to consider is lane changing. Lane changing models do exist \cite{lanechanging} \cite{lanechanging2},
but can be complex, requiring modeling of driver choices and gap acceptance for drivers. Peachtree is a two lane road,
so lane changes are possible. However, we will make the assumption that drivers by this point have already made any
discretionary lane changes and traffic is evened out between lanes. Also, we will assume left turning drivers will be
in the left lane already. Similarly, right turning drivers will already be in the right lane.
